---
title: "Machine Learning Project"
author: "Shrey"
date: "10/20/2020"
output: html_document
---
## Insert data and libraries
```{r setup, include=FALSE}
library(dplyr)
library(caret)
library(rpart)
library(randomForest)
training<-read.csv("pml-training.csv")
testing<-read.csv("pml-testing.csv")
dim(training)
set.seed(110)
```

## Manage the data

```{r manage}
training[training == ""] <- NA
training[training=="#DIV/0!"] <- NA
training[training=="<NA>"] <- NA

traindex <- createDataPartition(training$classe,p = 0.7,list = FALSE)
train <- training[traindex,]
test <- training[-traindex,]
```
Since there are many columns with NA values we remove them from analysis

```{r analysis, echo=FALSE}
train1 <- train[which(train$new_window == "no"),]
train1 <- train[!colSums(is.na(train)) > 0]
```
## Applying algorithms
We first try to use random forest algo as it can be used for both classification and regression and doesn't do overfitting
```{r algo}
model <-randomForest(classe ~. , data=train1[,-c(1:7)], method="class")
pred_test1 <- predict(model, test)
pred_train1 <- predict(model, train)

confusionMatrix(pred_train1, train$classe)
confusionMatrix(pred_test1, test$classe)
```
We see that random Forest algorithm works quite well in this scene,and since providing graphical analysis is tough in this, we will use this algorithm

Now we test our testing data
```{r test}
predict(model,testing)
```
We get these values
